Notes on generating initial models for mapping into {\tt MAESTRO}

### 2008-08-19 docs/initial_models/paper.tex
OK I think this is *finally* right for single level problems

Using the raw data, we need to generate model data at the same resolution as the base state.  Note that for spherical problems we set $\Delta r = \Delta x$.  We use a fortran subroutine to interpolate the raw data, yielding the model data, $\rho^{\model}, T^{\model}, p^{\model}$, and $X^{\model}$.  The fortran subroutine then uses an iterative procedure to modify the model data so that it is thermodynamically consistent with the {\tt MAESTRO} equation of state (EOS), and also satisfies our chosen hydrostatic equilibrium (HSE) discretization,

@@

The model data is not generated at run-time - it must be generated in advance of running any MAESTRO examples.  The inputs file points to the file containing the model data.

@@

\item Call the EOS to obtain a 1D $h^{\init} = h^{\init}(\rho^{\init},T^{\init},X^{\init})$.  Note that in the code, $p^{\init}$ is also overwritten, but the value of $p^{\init}$ does not change since we called $p^{\init} = p^{\init}(\rho^{\init},T^{\init},X^{\init})$ at the end of the previous fortran subroutine.
\item For plane-parallel problems, fill $\rho^{\init}, h^{\init}, X^{\init}$, and $T^{\init}$ onto a multifab to obtain the full state $\rho, h, X$, and $T$.  For spherical problems, fill $\rho^{\init}, p^{\init}$, and $X^{\init}$ onto a multifab to obtain the full state $\rho, p$, and $X$, and then call the EOS to obtain the full state $h,T = h,T(\rho,p,X)$.

@@

\item Perturb $T$, then compute $\rho,h = \rho,h(p^{\init},T,X)$.

@@

\item Compute $p_0$ using equation (\ref{HSE Discretization}).

@@

\subsection{Multilevel Case}
Again, we are given 

>>>>

Using the raw data, we need to generate model data with the same resolution as the base state.  Note that for spherical problems we set $\Delta r = \Delta x$.  We use a fortran subroutine to interpolate the raw data, yielding the model data, $\rho^{\model}, T^{\model}, p^{\model}$, and $X^{\model}$.  The fortran subroutine then uses an iterative procedure to modify the model data so that it is thermodynamically consistent with the {\tt MAESTRO} equation of state (EOS), and also satisfies our chosen hydrostatic equilibrium (HSE) discretization,

@@

The model data is not generated at run-time - it must be generated in advance of running any MAESTRO examples.  The inputs file should point to the file containing the model data.
\subsection{Multilevel Plane-Parallel}
We need to generate model data with the same resolution as the finest base state resolution.

@@

\item For plane-parallel problems, fill $\rho^{\init}, h^{\init}, X^{\init}$, and $T^{\init}$ onto a multifab to obtain the full state $\rho, h, X$, and $T$.  For spherical problems, fill $\rho^{\init}, p^{\init}$, and $X^{\init}$ onto a multifab to obtain the full state $\rho, p$, and $X$, and then call the EOS to obtain the full state $h,T = h,T(\rho,p,X)$.  Note that the multifab version of $p$ is temporary, and can be deallocated after this step.

@@

\item Perturb $T$, then compute $\rho = \rho(p^{\init},T,X)$.

@@

\item Compute $p_0$ using equation (\ref{HSE Discretization}), using $p_{0,r=0}$ as the initial condition.

@@
